### 2018-12-14 README.Rmd
update intro

While methods to interpolate multiple spatial data sets are currently available in the ArcGIS Suite and the `R` package `sf`, `areal` offers an intuitive assortment of options to validate, interpolate, and compare fields between a source and target data set.

## Installation
The development version of `areal` can be accessed from Github with `remotes`:

@@

```{r mixed}
# remove sf geometry
st_geometry(race) <- NULL

# create combined data
race %>%
  select(GEOID, TOTAL_E, WHITE_E, BLACK_E) %>%
  left_join(asthma, ., by = "GEOID") -> combinedData

@@

```{r sf-output}
aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", type = "extensive", 
               weight = "sum", output = "sf", "TOTAL_E", "WHITE_E", "BLACK_E")
```

>>>>

`areal` offers an intuitive assortment of options to validate, interpolate, and compare fields between a source and target data set. While methods for implementing areal weighted interpolation are available outside of the `R` ecosystem (ex - toolboxes in ArcGIS) and within `R` (the `sf` package's `st_interpolate_aw`) function, `areal` fills a niche by providing additional functionality not available in `sf` while taking advantage of the reproducibility of `R`.

`areal` currently implents only areal weighted interpolation, but a roadmap is being developed to add additional interpolation methods as well. This will be posted on the package's website before the initial CRAN release.

## Installation
### Installing Dependencies

You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package. Instructions vary significantly by operating system. For best results, have `sf` installed before you install `qualmap`. Other dependencies, like `dplyr`, will be installed automatically with `areal` if they are not already present.

### Installing areal
The development version of `areal` can be accessed from Github with `remotes`:

@@

```{r mixed}
# remove sf geometry
raceTable <- race
st_geometry(raceTable) <- NULL

# create combined data
raceTable %>%
  select(GEOID, TOTAL_E, WHITE_E, BLACK_E) %>%
  left_join(asthma, ., by = "GEOID") -> combinedData

@@

```{r sf-output}
aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID", type = "extensive", 
               weight = "sum", output = "sf", "TOTAL_E", "WHITE_E", "BLACK_E")
```
